The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-11-02 manuscript.Rmd
improve table legend, make subheadings bold

```{r records-table, results='asis'}
print.xtableList(institution_contributions, colnames.format = "multiple",
                 booktabs = TRUE, include.rownames = FALSE,
                 table.placement = "!ht")
```

>>>>

```{r records-table, results='asis'}
xtbl_small <- function(x) {
    glue::glue("{{\\footnotesize {x} }}")
}
xtbl_bold <- function(x) {
    glue::glue("{{\\bfseries {x} }}")
}
print.xtableList(institution_contributions, colnames.format = "multiple",
                 booktabs = TRUE, include.rownames = FALSE,
                 sanitize.subheadings.function = xtbl_bold, 
                 sanitize.message.function = xtbl_small, 
                 table.placement = "!ht")
```
